Efficient Coalition Formation for Web Services

### 2013-03-01 papers/coalition/coalition.tex
Changes

{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by: 
\begin{equation}\label{eq:shapley}
\sum_{S \subset N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
\end{equation}

Shapley value is a unique and fair solution concept for payoff distribution between players or agents.

\subsubsection{Shapley value}
Shapley value is a solution concept for payoff vector, where it tries to achieve fairness
\subsubsection{Core}
123

>>>>

{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by\cite{shapley_value}: 
\begin{equation}\label{eq:shapley}
\sum_{S \subset N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
\end{equation}

Shapley value is a unique and fair solution concept for payoff distribution between agents. It basicly rewards agents with amount of marginal contribution they have to the coalition.

{\bf Definition 1 (Core)}
